Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-24 Thesis/chapter/063-discussion.tex
free write phase 2

\subsection{Hindsight is easier than foresight}
%\subsection{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%todo{british or US?} 
This subsection will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
Firstly, the \textit{research, exploration and design phase}, followed by the \textit{narrowing, pre-optimisation and constraint phase}, thereupon the \textit{optimisation, modelling and data generation phase} and finally the \textit{evaluation, interpretation and outlook phase}. 
%\subsubsection{Research, exploration and design phase}
%\subsubsection{Narrowing, pre-optimisation and constraint phase}
%\subsubsection{Optimisation, modelling and data generation}
%\subsubsection{Evaluation, interpretation and outlook phase}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Research, exploration and design phase}
\td{freewriting}: \textbf{Scrutinize everthing!} At the beginning of a project it is importatnt 
to get a feel. I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that no matter how much I improved it, it was still bad. 
I only noticed this after trying out another recipe. 
My tipp here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
This will get you a "feel" of what works and what not. 
Thinking back to some design classes I took for data visualization: create as many and different designs as possible. 
Check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

@@

A general experimental procedure was stated by Cherkassky and Mulier\cite{cerkassky1998learning}:

@@

@@

\td{This section is about 3. DAta Generation and Experiment Design from cherkessky's list. }

@@

%-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest. Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2007}

@@

@@

>>>>

\subsection{Hindsight is easier than foresight}
%\subsection{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%todo{british or US?} 
This subsection will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
Firstly, the 
\ref{sec:phase1} \textit{\nameref{sec:phase1}}, followed by the 
\ref{sec:phase2} \textit{\nameref{sec:phase2}}, thereupon the 
\ref{sec:phase3} \textit{\nameref{sec:phase3}} and finally the 
\ref{sec:phase3} \textit{\nameref{sec:phase4}}. 
%\subsubsection{Research, exploration and design phase}
%\subsubsection{Narrowing, pre-optimisation and constraint phase}
%\subsubsection{Optimisation, modelling and data generation}
%\subsubsection{Evaluation, interpretation and outlook phase}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Research, exploration and design phase}
\label{sec:phase1}
\td{freewriting}: \textbf{Scrutinize everthing!} At the beginning of a project it is importatnt 
to get a feel. I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that no matter how much I improved it, it was still bad. 
I only noticed this after trying out another recipe. 
My tipp here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
This will get you a "feel" of what works and what not. 
Thinking back to some design classes I took for data visualization: create as many and different designs as possible. 
Check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

@@

A general experimental procedure was stated by Cherkassky and Mulier\cite{cherkassky1998learning}:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\label{sec:phase2}
After having decided on a base recipe, it is important to define limits and decrease the number of independent varibles. 
The later is more important due to the curse of dimensionality\cite{cherkassky1998learning}, 
which states that with increasing dimensionality it get exponentially more difficult to arrive at the same density of datapoints. 
By excluding input variables from the model 
the complexity of the model can be drastically reduced. 
This leads to more information which can be extrated from the remaining data, 
be it in more detail of the dependence or higher confidence interval. 
A good measure to compare with literature and other methods is the \gls{epv}. 
In this work there around 5~\gls{epv}, which is pretty low. 
This is ofcourse not just as straight forward as suggested. 
How does one decide which variables to keep and which to incorporate into the model and which to discard? 
There is the intuitive (expert) way and the mathematical way.
mathematical ways include: pca, step-wise regression 
%
Additionally having wide limit can be an advantage when the data is noisy and the dependence is not too complicated.
"By moving the samples to the boundaries of the design space, the effect of the random term is reduced\cite{giunta2003overview}."
%
There are two opposing principles which can be followed: 
By introducing a lot of variables into a model presupposes that they and their interactions (!) have a statistically significant effect.\cite{gunst2009fractional}.
On the other hand a model can be used to tell if a variable exerts an influence. 
%
One regime where overfitting occurs is when there are to many parameters to be fitted with not enough data. 
Overfitting happens in the regime where to many parameters are fitted with not enough data. 
%
Another step/deed which is well placed in this phase is the estimating the error by reproducing a singel sample a certain number of times. 
Where the number will then be higher than during optimisation 
%
%\td{This section is about 3. DAta Generation and Experiment Design from cherkessky's list. }

@@

%-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest. Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2009}

@@

\label{sec:phase3}

@@

\label{sec:phase4}
